Cache Oblivious B-trees

### 2011-12-07 paper.tex
more progress on concurrency paper

@@

@@

The concurrency protocol works as follows. Any of the non-blocking primitives
are initiated by denoting the cell in question with the marker. If a process
ever encounters a cell with a marker, it drops what it is doing and first helps
to complete the operation. The implementation of the non-blocking primitives
is spelled out in more detail in \cite{BenderFiGi05}, but the basic idea is
using LL/SC to detect when concurrent operations are on-going.

@@

>>>>

\subsubsection{Complexity}
Sequential search takes $O(\log_B{N} + \log_{\alpha}{\log_2{B}})$ block
transfers (with high probability). The probabilistic bound comes from the
probabilistic key promotion property. The intuition behind the proof of this
bound comes from the argument that when the tree has height $h =
\Omega(\log_{\alpha}{\log_2{\log_2{N}}})$, then the total number of keys in the
tree is $O(2^{\alpha^h})$. The proof is then completed by summing over the
range of $h$ which is probabilistic $O(\log_{\alpha}{\log_2{N}})$, the access
time from some level $h$ to find the correct child.

Sequential insert takes $O(\log_B{N} + \log{\alpha}{\log_2{B}})$ block
transfers (in expectation). This proof is constructed in a similar 
fashion as the search proof: consider inserting a tree at some height $h$.
By noting that the probability a particular node reaches height $h$
is $2^{-(\alpha^h-1)/(\alpha-1)}$, a summation over all levels
of the cost of rebuilding a node yields the time-bound.

@@

% TODO: can somebody check this time-bound? seems kind of bad
Sequential search time-bounds are not presented in the paper,
but presumably since search is a static CO tree lookup followed
by a scan, the time bound is $O(\log_{B}{N} + {\log_2{N}}/{B} + 1)$.

Sequential insert is $O(\log_{B}{N} + \log_2^2{N}/{B} + 1)$. The proof
is based off an accounting argument which places $\Theta(\log_2^2{m}/B)$
dollars in each array slot. The proof is not presented in any detail in the
paper, but rather it is a slightly-modified version of the proof presented
in \cite{Katriel02}.

@@

The concurrency protocol works as follows. Any of the non-blocking primitives
are initiated by denoting the cell in question with the marker. If a process
ever encounters a cell with a marker, it drops what it is doing and first helps
to complete the operation. When the originating process gets context-switched
back in, any SCs will fail, and then the process can check to see if the
operation was already completed. The implementation of the non-blocking
primitives is spelled out in more detail in \cite{BenderFiGi05}, but the basic
idea is using LL/SC to detect when concurrent operations are on-going.

@@

\section{Conclusion}
